Followers Are Not Enough: Beyond Structural Communities in Online Social Networks

### 2014-03-31 paper-for_arxiv/conclusions.tex
moving around and files

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent. The questions posed about a network \emph{a priori} have a strong impact on the communities observed.  Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone. By varying the questions we asked about the network and then deriving weighting schema to answer that particular question, we found that community structure differed across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale in interesting ways.

@@

To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions. In particular, conversations (e.g. retweets and mentions) and topics (e.g. hashtags) tended to be most highly concentrated within communities. We found this to be the case even when the communities were defined by a different criteria from the edge weights.

@@

At first glance the boundaries defined by the activity-based communities derived from the transfer entropy weighting seemed less meaningful. However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: influence tended to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social} for online social networks. This means that our novel use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.

>>>>

In this study, we have demonstrated that the communities observed in online social networks are highly question-dependent. The questions posed about a network \emph{a priori} have a strong impact on the communities observed.  Moreover, using different definitions of \emph{community} reveal different and interesting relationships between users. More importantly, we have shown that these different views of the network are not revealed by using the structural network or any one weighting scheme alone. By varying the questions we asked about the network and then deriving weighting schema to answer each question, we found that community structure differed across community types on both the macro (e.g. number of communities and their size distribution) and micro (e.g. specific memberships, comemberships) scale in interesting ways.

@@

To verify the validity of these communities we demonstrated that boundaries between communities represent meaningful internal/external divisions. In particular, conversations (e.g. retweets and mentions) and topics (e.g. hashtags) tended to be most highly concentrated within communities. We found this to be the case even when the communities were defined by a different criterion from the edge weights under study.

@@

At first glance the boundaries defined by the activity-based communities derived from the transfer entropy weighting seemed less meaningful. However, upon further investigation our novel use of transfer entropy for the detection of activity-based communities highlighted an important fact about this social network: influence tended to be higher across community boundaries than within them. This result echos the `strength of weak ties' theory from~\cite{granovetter1973strength}, which has found empirical support in~\cite{grabowicz2012social} for online social networks. This means that our use of transfer entropy not only defines boundaries that are meaningful divisions between communities but also illustrates that users who have a strong influence on a community need not be a member of that community.

### 2014-03-31 paper-for_arxiv/results.tex
moving around and files

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/comm_sizes_ecdf_loglog.pdf}
\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/nmi_singletons.pdf}
\caption{The normalized mutual information between the coverings inferred from the different community types. Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/edge-types.eps}
\caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow). We focus on the internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) edges. For a given focal community, all other edges (grey) are not considered.}
\label{Fig-edge_types}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{figures/comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}. The community is defined by user interactions, and the edge weights are determined by topic similarity. The dashed vertical lines indicate the median weight for each type of edge. Note the logarithmic scale on the horizontal axis.}
\label{Fig-dist_across_community}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{comm_sizes_ecdf_loglog.pdf}
\caption{The proportion of communities greater than $c$ in size, across the different community types. Note the logarithmic scale on the horizontal and vertical axes.}
\label{Fig-community_size_distribution}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{nmi_singletons.pdf}
\caption{The normalized mutual information between the coverings inferred from the different community types. Community type 0 corresponds to the structural communities, community types 1 through 6 correspond to the activity-based communities with lag 1 through 6 transfer entropies, community type 7 corresponds to the topic-based communities, and community types 8, 9, and 10 correspond to the interaction-based communities using mentions, retweets, and both mentions and retweets. Values of normalized mutual information close to 1 indicate similarity in the community structure, while values close to 0 indicate dissimilarity. The normalized mutual information is computed with singletons and orphan nodes included.}
\label{Fig-compare_coverings}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{edge-types.eps}
\caption{An example of the edges considered in determining the edge weight distribution for a given community (the focal community is in yellow). We focus on the internal-to-internal (red), internal-to-external (green), and external-to-internal (blue) edges. For a given focal community, all other edges (grey) are not considered.}
\label{Fig-edge_types}
\end{figure}

@@

\begin{figure}[ht]
  \centering
\includegraphics[width=0.50\textwidth]{comm0_labels-mention-retweet_weights-hashtag-ecdf.pdf}
\caption{The proportion of edges with a weight at least as large as the weight on the horizontal axis, across the types of edges described in Figure~\ref{Fig-edge_types}. The community is defined by user interactions, and the edge weights are determined by topic similarity. The dashed vertical lines indicate the median weight for each type of edge. Note the logarithmic scale on the horizontal axis.}
\label{Fig-dist_across_community}
\end{figure}
